\cvsection{Intro Letter}

Dear Hiring Manager,

\smallskip

As a technical professional passionate about delivering exceptional IT support while maintaining high standards of system administration, I'm excited to apply for the Systems Administrator position at Fortis.
Your commitment to transforming payments technology resonates strongly with my background in providing fast and effective technical assistance while developing innovative solutions.

\smallskip

With over two years of experience as a Senior Technician at ACT Computers, I've developed a strong foundation in providing comprehensive technical support across diverse systems.
My current role has equipped me with expertise in remote troubleshooting, system configuration management, and hardware/software maintenance - skills that align perfectly with your requirements.
I've successfully implemented efficient documentation systems for employee workflows and managed customer computers via Remote Monitoring and Management tools, demonstrating my ability to adapt technology solutions to business needs.

\smallskip

My technical background, particularly in Windows desktop operating systems and Microsoft ecosystem tools, positions me well for your environment.
While my primary focus has been on Windows systems, my experience with Linux and familiarity with cross-platform environments ensures versatility in supporting diverse technical infrastructures.
My proficiency in PowerShell scripting and system automation will serve me well in managing your Office365 tenant and Intune MDM implementation.

\smallskip

What excites me most about this opportunity is the chance to combine my technical expertise with my passion for problem-solving in a dynamic environment.
At ACT Computers, I've consistently demonstrated my ability to handle high-pressure situations while maintaining excellent customer service standards.
I'm confident that my analytical mindset, combined with my experience in documenting resolutions and tracking technical issues, would make me a valuable asset to your team.

\smallskip

I appreciate Fortis's commitment to innovation and excellence in the FinTech space.
Your emphasis on collaborative problem-solving and employee growth aligns with my own professional values.
I'm particularly drawn to the opportunity to work with cutting-edge payment technologies while ensuring seamless technical operations for your team.

\smallskip

Thank you for considering my application.
I'd welcome the opportunity to discuss how my technical expertise and support experience could contribute to Fortis's continued success.
Please feel free to contact me at your convenience.

\smallskip

Best regards,
Justin Patera

