\cvsection{Intro Letter}
%% \parindent = 20 pt

Dear Hiring Manager,

\smallskip

I am excited to apply for the Software Engineer position at Medical Data Systems, where I can leverage my passion for innovative solutions.
With 8 years of experience in software development and a proven track record of creating efficient, scalable systems, I believe I would be an excellent fit for your team in Vero Beach.

\smallskip

Throughout my career, I have developed strong skills in .NET technologies, particularly C\#, along with proficiency in backend SQL queries and scripting.
At Level 3 Inspection, I worked on various small-to-medium projects, focusing on code development and debugging.
One of my standout projects was the Haz Ion 3D Structured Light scanner, where I wrote operational code involving complex data structures, timing routines, and algorithms to process hundreds of images in mere seconds.
This project demonstrates my ability to create applications that meet specified requirements and conduct thorough unit-testing, aligning well with MDS's need for developing custom software applications.

\smallskip

Additionally, I have extensive experience in data automation.
From March 2018 to June 2018, I created automation to take data from Michigan, automatically uploading, post-processing, and outputting reports in CSV, Excel, and Google Docs concurrently.
This project showcases my ability to interpret business requirements, complete system enhancements, and participate in integration testing for development efforts.

\smallskip

My experience extends beyond coding.
At ACT Computers, I have been generating documentation for employee workflows since May 2022, demonstrating my ability to communicate clearly and concisely in writing.
This skill will be valuable in interacting with both Business and IT partners at MDS to define, understand, and evaluate business requirements.

\smallskip

I possess excellent analytical skills, evident in my work on the Natural Light Labeling (NLL) and ApZ laser technologies at Premier Citrus.
These projects involved complex problem-solving and adapting to new technologies quickly, traits that will serve me well in identifying root causes of problems and providing options for resolution at MDS.

\smallskip

Furthermore, my experience in fast-paced environments, such as at Level 3 Inspection and ACT Computers, has honed my ability to multitask effectively and function flexibly under pressure.

\smallskip

Thank you for your time and consideration.
I am excited about the opportunity to contribute to Medical Data Systems' continued success and growth.
I look forward to discussing how my skills and experience align with your team's needs.

\smallskip

Have an awesome day!

\smallskip

Justin Patera

