\cvsection{Intro Letter}

To Whomever is Reading This

\smallskip

I hope you are doing awesome today!
I have been working as a computer technician professionally for over 20 years.
Mostly in support of small businesses, but also individual customers.
While a lot of what I have worked on for individuals is break-fix kind of stuff (virus removal, software install, password reset) I am also highly familiar with small business IT and RMM services.

\smallskip

While working at ACT computers, I am the go-to indiviual for a handful of clients.
Managing their setup, making recommendations, and

\smallskip

During my work on the ``Haz Ion 3D Structured Light scanner,'' I primarily focused on implementing the core functionality for capturing 3D images.
This involved processing acquired images using calibration data to analyze projected patterns on surfaces and reconstruct 3D models.
While traditional structured light scanners often employ Gray Code patterns, this project utilized a proprietary setup involving series of sine-wave projections.
Despite my limited familiarity with the underlying mathematics, I successfully adapted MatLab code into efficient C++ GPU implementations.
These components were seamlessly integrated with a main controller program written in Common Lisp, demonstrating effective inter-language collaboration in a real-world application.

\smallskip

The ``Data Automation'' pipeline I developed enabled project owners in Michigan to receive real-time updates of scanned parts.
This system spanned two geographical locations: Michigan, where initial scans were conducted, and Florida, where data processing and analysis took place.
Scan data was collected on-site in both Michigan and Florida before being transferred to our servers in Florida for processing through a custom pipeline.
After processing, the resulting CSV files were automatically queried and updated in a Google spreadsheet accessible to the customer, providing instant visibility into project progress.
Notably, I leveraged Erlang as the primary language for this project due to its exceptional reliability, meeting a high-availability requirement.

\smallskip

Thank you for considering my application.
I would welcome the opportunity to discuss how my skills and experience would benefit SpaceX and its mission.
Please feel free to contact me at (772) 643-3621 or via email at serialhex@gmail.com to arrange a convenient time for us to speak further.

\smallskip

Have an awesome day!

Justin Patera
