\cvsection{Intro Letter}
\parindent = 20 pt

\noindent To Whom it may concern.

I found this listing, and it sounds very interesting.
The idea of designing robots to do menial tasks, like mow lawns, is awesome.
I know it's not a ground-breaking innovation - people have been using machines for millennium - but it is refreshing that technology is being used to make peoples lives easier, not harder.

While it may not be readily apparent, I do have some experience working outdoors.
For a few months between jobs I worked at Big Little Guy pressure washing in the hose management department (I ran the hose around, making sure it wasn't kinked and the job could get done effectively).
The owner's name is Richard Blunt and can be reached at (772) 480-6880 for a reference.

As a homeowner, I have been practically forced to acquaint myself with various power tools.
Doing so has enabled me to fix a number of issues around the house, including fixing my mailbox.
I also built a simple computer desk for myself.
There was also a time I assisted a friend building a custom projector mount that hung from the railing of a staircase.

And, of course, I do my own lawn work.

Working in software development I am familiar with needing detail and have worked with other engineers in solving problems.
When working at Level 3 Inspection I worked with mechanical engineers to ensure the data collected and processed was exactly what they needed.
Problem solving is something I enjoy, especially in a team setting where we can divide up the problems to solve them quicker, or troubleshoot together for particularly challenging problems.

Thank you for your consideration, and have an awesome day!

Justin Patera

