\cvsection{Intro Letter}

Dear Danielle Elliott,

\smallskip

I hope this letter finds you well.
My name is Justin Patera, and I am writing to express my strong interest in the System Administrator position currently open at the Vero Beach Museum of Art.
With over 20 years of experience in computer and network repair, I believe my skills and background align perfectly with the requirements of this role.

\smallskip

As a seasoned technician, I bring extensive experience in maintaining and troubleshooting computer systems, networks, and software applications.
My expertise spans hardware repair, software installation, and network configuration.
I am confident that my technical knowledge and hands-on experience would be valuable assets to your team.

\smallskip

Throughout my career, I have consistently demonstrated my ability to:

\begin{itemize}
  \item Troubleshoot complex technical issues efficiently
  \item Provide excellent customer service and support
  \item Maintain accurate records and documentation
  \item Collaborate effectively with staff members
\end{itemize}

\smallskip

In my time at ACT Computers, where I have served as Senior Technician since May 2022, has honed my skills in repair, scheduling, and generating documentation.
Additionally, at Level 3 Inspection as a Computer Programmer has given me valuable experience in fulfilling project requirements set by management.

\smallskip

I am particularly excited about the opportunity to apply my technical expertise to support the operations of the Vero Beach Museum of Art.
I understand the importance of reliable technology infrastructure in supporting artistic and educational programs, and I am eager to contribute to maintaining the museum's IT systems.

\smallskip

Thank you for considering my application.
I would welcome the opportunity to discuss how my skills and experience align with the needs of the Vero Beach Museum of Art.
Please feel free to contact me at (772) 643-3621 or via email at serialhex@gmail.com to arrange a convenient time for us to speak further.

\smallskip

Have an awesome day!

Justin Patera

